Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-06-24 ms.tex
beginnings of a sensitivity table, and comments on introductory material

@@

One important factor in modeling the radio emission due to the interaction between stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
The number density of stellar wind, $n$, can be expressed as
%%%%%%%%%% 
\begin{equation}
n = \frac{\dot M_\star}{4\pi a^2 m_p v}
\label{eq:n}
\end{equation}
%%%%%%%%%% 
where $\dot M_\star$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.

@@

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}. 
The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
\end{eqnarray}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.

@@

In reality, the total power of Jovian auroral emission highly varies in time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}. 
Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
\memoYF{reconsidering...}

@@

>>>>

\definecolor{DarkGreen}{rgb}{0.0, 0.6, 0.0}
\def\memoTM#1{\color{DarkGreen}$[${\bf #1}$]$ \color{black}}

@@

One important factor in modeling the radio emission due to the interaction between stellar wind and the planetary magnetic field is the density and velocity of stellar wind. 
The number density of \memoTM{electrons in the (?)} stellar wind, $n$, can be expressed as
%%%%%%%%%% 
\begin{equation}
n = \frac{\dot M_\star}{4\pi a^2 m_p v}
\label{eq:n}
\end{equation}
%%%%%%%%%% 
where $\dot M_\star$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.

@@

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}. 
The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
\end{eqnarray}
\memoTM{Somekind of plot of the typical ranges of these quantities might be useful/illustrative.}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.

@@

In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}. 
Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
\memoYF{reconsidering...}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htdp]
\caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
\begin{center}
\begin{tabular}{c|ccc} \hline \hline\\[-0.5pc]
Instrument & Band & Sensitivity & Time  \\[.25pc]
 &  & $\mu$Jy~hr$^{1/2}$ &  hr \\[0.25pc] 
\hline\\[-0.5pc]
GMRT & 220~MHz &  \\
HERA  & 70~MHz  &  &  \\
LOFAR  & 120~MHz  &  &  \\
LWA  & 70~MHz  &  &  \\
SKA  & 200~MHz  &  &  \\
UTR-2 & & & \\
VLA  & P-band (270-430~MHz)  \\ \hline
\end{tabular}
\end{center}
\label{tab:sens}
\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
telescopes that can reach this in less than XX hours without
being confusion limited.}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{deluxetable}{l|lll}
%\tablecolumns{4}
%\tablewidth{0pt}
%\tabletypesize{\scriptsize}
%\tablecaption{Detectability of Hot Jupiters with Current and Future Radio Telescopes}
%\tablehead{ Instrument & Band & Sensitivity & Time  \\ 
% &  & $\mu$Jy~hr$^{1/2}$ &  hr} 
%\startdata 
%GMRT & 220~MHz   &  & \\
%SKA  & 200~MHz)  &  &  \\
%VLA  & P-band (270-430~MHz)  &  & 
%\enddata
%\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
%telescopes that can reach this in less than XX hours without
%being confusion limited.}
%\label{tab:sens}
%\end{deluxetable}
